One-step, three-factor authentication with in-ear EEG

### 2016-12-03 paper.tex
Added data analysis section

% Created 2016-11-30 Wed 17:09
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Max Curran and Nick Merrill}
\date{\today}
\title{One-step, three-factor authentication with in-ear EEG}
\hypersetup{
 pdfauthor={Max Curran and Nick Merrill},
 pdftitle={One-step, three-factor authentication with in-ear EEG},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.0.50.2 (Org mode 9.0.1)}, 
 pdflang={English}}
\begin{document}

\maketitle
\begin{abstract}
We propose the first research study of one-step three-factor authentication.
Specifically we seek to demonstrate its feasibility and quantify its performance
using Ear EEG (electroencephalogram). By performing a single mental task, our
user will be able to present three authenticators at once – a knowledge factor
(their chosen secret thought and/or mental task), an inherence factor (their
brainwave signals), and a possession factor (the EEG sensing earpiece that is
custom-fitted to their ear). We will build the custom-fit Ear EEG earpieces and
conduct an experimental study to evaluate the accuracy and usability of this
authentication method.
\end{abstract}
\section{Introduction and Motivation}
\label{sec:orgd88076b}

@@

\section{Related Work}
\label{sec:orge0e46dc}
The use of EEG as a biometric signal for user authentication has a short history.
In 2005, Thorpe et al. motivate and outline the design of a passthoughts system,
where users authenticate by thinking of a passthought rather than typing in a
password [6]. Since 2002, a number of independent groups have achieved 99-
100\% authentication accuracy using multi-channel sensors placed on the scalp
[7-10]. In 2013, our group showed that 99\% authentication accuracy can also be
achieved using a consumer-grade single-channel sensor [2]. In particular, the
lack of signal diversity from multiple EEG channels can be overcome by allowing
the users to choose their own personalized passthoughts (e.g., sing their favorite
song in their head). There are two significant consequences of this result. First,
the passthoughts approach is no longer constrained by the high cost (\textasciitilde{}\$10k’s)
and low usability (gel-based electrodes; aesthetic challenges of an EEG cap) of
medical-grade multi-channel devices. Second, because users can choose and
easily change their secret mental task, this approach can support one-step two-
factor authentication [1] via the simultaneous presentation of the inherence factor
(brainwave signatures due to the unique folding structures of the cortex) and the
knowledge factor (the secret mental task).

@@

\section{Proposed project}
\label{sec:org6246122}

@@

\section{Research plan}
\label{sec:org5e36c1a}

@@

For authentication analysis, we will build upon the analysis methodology and
tools from our previous studies. We will apply the logarithmic binning technique
that we have developed in [5] to the EEG power spectrum data during the signal
pre-processing step. We will then apply machine learning to train and test a
support vector classifier as in [4]. We will compare the results against the
threshold-based authentication protocol based on cosine similarity as in [2,3].
A key change for this study is that we will be able to collect up to 8 separate
channels of EEG data, including multiple channels from each ear. This is in
contrast to our previous studies, where we collected only a single channel of
EEG, either on the prefrontal cortex (FP1) location or in the ear canal. Therefore,
we will need to develop new analytic techniques to both (i) assess improvements
in authentication accuracy due to the increased channels of data, and (ii) assess
relative contributions of individual electrode locations to authentication accuracy.
Finally, we will evaluate the usability of custom-fit Ear EEG authentication along
several dimensions. They include the comfort and fit of the earpieces, the
preparatory steps of using the devices, the ease and repeatability of the
authentication tasks, and the recall rates of the personal secrets.
\section{{\bfseries\sffamily TODO} Preliminary results}
\label{sec:orgb471f1b}

We performed a very small pilot study (n=2) to better understand how feasible 
our project would be. Our cursory analysis indicates that we can successfully
detect EEG signals from the ear (Section 5.1), that these signals can be used
for reliable authentication among two people (Section 5.2), and that the success
of the authenticator relies on the user's chosen secret, and not just the inherence
factor of the user's unique signal (Section 5.3).

\subsection{{\bfseries\sffamily TODO} Validation}
\label{sec:orgdae54ad}
\subsection{{\bfseries\sffamily TODO} Authentication performance}
\label{sec:org14de4b9}
\subsection{Disentangling inherence and knowledge}
\label{sec:org91c37b4}

@@

\begin{center}
\begin{tabular}{lrrr}
Task & Right ear & Left ear & fp1\\
\hline
speech & 0.311 & 0.116 & 0\\
face & 0.355 & 0.055 & 0\\
breathe & 0 & 0.240 & 0\\
listennoise & 0.322 & 0.078 & 0\\
song\(_{\text{o}}\) & 0 & 0.166 & 0\\
song & 0 & 0.211 & 0\\
sequence & 0.433 & 0 & 0\\
listentone & 0 & 0.333 & 0\\
breathe\(_{\text{o}}\) & 0.254 & 0.129 & 0\\
sport & 0.222 & 0.135 & 0\\
\hline
\textbf{p-value} & \textbf{*0.0076} & \textbf{*0.009} & N/A\\
\end{tabular}
\end{center}
Our low p-values (Table 3) indicate that the passthought, as well as the inherence
factor associated with the custom-fit EEG earbud, both contribute to the classifier
performance discussed in Section 5.2. We are confident, then, in our claim that this work
could potentially yield multiple-factor authentication in a single step. However, we
will need to collect a great deal more data to substantiate this claim rigorously.

\section{Schedule and Budget}
\label{sec:org1590dbf}
We propose a 12-month schedule with two graduate students working on the
project:

\begin{itemize}
\item Months 1-6: hardware development for custom-fit earpiece; integration with OpenBCI; testing
\item Months 1-6: software integration between OpenBCI, PsychoPy, and Indra; design of new authentication tasks and implementation in PsychoPy
\item Months 7-8: experimental data collection
\item Months 9-12: data analysis; write and submit research papers
\end{itemize}
\section{References}
\label{sec:org14ba974}

[1]
J. Chuang, One-Step Two-Factor Authentication with Wearable Bio-Sensors, Workshop on
"Who are you?! Adventures in Authentication" (WAY'14), 10th USENIX Symposium on
Usable Privacy and Security (SOUPS'14), 2014.

[2]
J. Chuang, H. Nguyen, C. Wang, B. Johnson, I Think, Therefore I Am: Usability and
Security of Authentication Using Brainwaves, Workshop on Usable Security (USEC'13),
17th Int. Conference on Financial Cryptography and Data Security (FC’13), 2013.

[3]
B. Johnson, T. Maillart, J. Chuang, My Thoughts are Not Your Thoughts: Robustness of
Brainwave Signal Authentication Against Impersonation Attacks, Workshop on Usable
Privacy \& Security for wearable and domestic Ubiquitous Devices, ACM UbiComp, 2014.

[4]
M. Curran, J. Yang, N. Merrill, J. Chuang. Passthoughts Authentication with Low Cost
EarEEG. Proc. 38th Intl. Conf. of IEEE Engineering in Medicine and Biology Society
(EMBC 2016), Aug. 2016.

[5]
N. Merrill, Maillart, Johnson, J. Chuang, Improving Physiological Signal Classification Using
Logarithmic Quantization and a Progressive Calibration Technique, Proc. 2nd Intl. Conf. on
Physiological Computing Systems (PhyCS'15), Feb. 2015.

[6]
J. Thorpe, P. van Oorschot, and A. Somayaji. Pass-thoughts: Authenticating with our
minds. In Proceedings of the New Security Paradigms Workshop (NSPW), 2005.

[7]
M. Poulos, M. Rangoussi, N. Alexandris, and A. Evangelou. Person identification from the
EEG using nonlinear signal classification. Methods of Information in Medicine, 2002.

[8]
S. Marcel and J. del R. Millan. Person authentication using brainwaves (EEG) and
maximum a posteriori model adaptation. IEEE Transactions on Pattern Analysis and
Machine Intelligence, 29(4), April 2007.

[9]
R. Palaniappan. Two-stage biometric authentication method using thought activity brain
waves. International Journal of Neural Systems, 18(1):59–66, 2008.

[10]
C. Ashby, A. Bhatia, F. Tenore, and J. Vogelstein. Low-cost electroencephalogram (EEG)
based authentication. In Proc. of 5th Int. IEEE EMBS Conf. on Neural Engineering, 2011.

[11]
D. Looney, C. Park, P. Kidmose, M. L. Rank, M. Ungstrup, K. Rosenkranz, and D. P.
Mandic, “An in-the-ear platform for recording electroencephalogram,” in Proc. Int. Conf.
IEEE Eng. Med. Biol. Soc., 2011, pp. 6682–6885.

[12]
D. Looney, P. Kidmose, C. Park, M. Ungstrup, M. Rank, K. Rosenkranz, and D. Mandic,
“The in-the-ear recording concept,” IEEE Pulse, vol. 3, no. 6, pp. 32–42, Nov./Dec. 2012.

[13]
P. Kidmose, D. Looney, M. Ungstrup, M.L. Rank, D.P. Mandic, “A study of evoked
potentials from ear-EEG,” IEEE Trans. Biomed. Eng. 60(10), pp. 2824–2830, 2013.

[14]
P. Kidmose, D. Looney, and D. P. Mandic, “Ear-EEG from generic earpieces: a feasibility
study,” in Proc. Int. Conf. IEEE Eng. Med. Biol. Soc., 2013, pp. 543-546.

[15] The Aware. \url{http://efitaware.com} [Online; accessed 22-Oct-2016].

[16] F. Monrose and A. Rubin. Authentication via keystroke dynamics. In Proceedings of the 4th
ACM conference on Computer and communications security, pages 48–56. ACM, 1997.

[17]
K. Stevens et al. Speaker authentication and identification: a comparison of spectrographic
and auditory presentations of speech material. The Journal of the Acoustical Society of
America 44.6 (1968): 1596-1607.

[18] Nymi. \url{https://nymi.com} [Online; accessed 22-Oct-2016].

[19] E. Strickland. In-Ear EEG Makes Unobtrusive Brain-Hacking Gadgets a Real Possibility.
IEEE Spectrum, 7/7/2016.

[20]
N. Merrill, M. Curran, J. Yang, J. Chuang. Classifying Mental Gestures with In-Ear EEG.
Proc. 13th IEEE Intl. Conf. on Wearable and Implantable Body Sensor Networks (BSN
2016), Jun. 2016.

[21]
E. Sedenberg, J. Chuang, D. Mulligan. Designing Commercial Therapeutic Robots for
Privacy Preserving Systems and Ethical Research Practices Within the Home. Intl. J. of
Social Robotics, Aug. 2016.

[22] E. Sedenberg et al. A Window into the Soul: Biosensing in Public. Under review, 2017.

[23] R. Wong et al. “All that happens must be known”: Eliciting Values and Conceptions of
Privacy using Science Fiction. Under review, 2017.

[24]
R. Wong et al. Real-Imaginary Entanglements: Using Science Fiction and Design Fiction to
Explore and Question Sensing and Tracking Technologies. Under review, 2017.
\end{document}

>>>>

% Created 2016-12-02 Fri 17:24
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Max Curran and Nick Merrill}
\date{\today}
\title{One-step, three-factor authentication with in-ear EEG}
\hypersetup{
 pdfauthor={Max Curran and Nick Merrill},
 pdftitle={One-step, three-factor authentication with in-ear EEG},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.0.50.2 (Org mode 9.0.1)}, 
 pdflang={English}}
\begin{document}

\maketitle
\begin{abstract}
We propose the first research study of one-step three-factor authentication.
Specifically we seek to demonstrate its feasibility and quantify its performance
using Ear EEG (electroencephalogram). By performing a single mental task, our
user will be able to present three authenticators at once – a knowledge factor
(their chosen secret thought and/or mental task), an inherence factor (their
brainwave signals), and a possession factor (the EEG sensing earpiece that is
custom-fitted to their ear). We will build the custom-fit Ear EEG earpieces and
conduct an experimental study to evaluate the accuracy and usability of this
authentication method.
\end{abstract}
\section{Introduction and Motivation}
\label{sec:org2e9e5c0}

@@

\section{Related Work}
\label{sec:orgffd9d9b}
The use of EEG as a biometric signal for user authentication has a short history.
In 2005, Thorpe et al. motivate and outline the design of a passthoughts system,
where users authenticate by thinking of a passthought rather than typing in a
password [6]. Since 2002, a number of independent groups have achieved 99-
100\% authentication accuracy using multi-channel sensors placed on the scalp
[7-10]. In 2013, our group showed that 99\% authentication accuracy can also be
achieved using a consumer-grade single-channel sensor [2]. In particular, the
lack of signal diversity from multiple EEG channels can be overcome by allowing
the users to choose their own personalized passthoughts (e.g., sing their favorite
song in their head). There are two significant consequences of this result. First,
the passthoughts approach is no longer constrained by the high cost (\textasciitilde{}\$10k’s)
and low usability (gel-based electrodes; aesthetic challenges of an EEG cap) of
medical-grade multi-channel devices. Second, because users can choose and
easily change their secret mental task, this approach can support one-step two-
factor authentication [1] via the simultaneous presentation of the inherence factor
(brainwave signatures due to the unique folding structures of the cortex) and the
knowledge factor (the secret mental task).

@@

\section{Proposed project}
\label{sec:org3384355}

@@

\section{Research plan}
\label{sec:org126c1a5}

@@

For authentication analysis, we will build upon the analysis methodology and
tools from our previous studies. We will apply the logarithmic binning technique
that we have developed in [5] to the EEG power spectrum data during the signal
pre-processing step. We will then apply machine learning to train and test a
support vector classifier as in [4]. We will compare the results against the
threshold-based authentication protocol based on cosine similarity as in [2,3].
A key change for this study is that we will be able to collect up to 8 separate
channels of EEG data, including multiple channels from each ear. This is in
contrast to our previous studies, where we collected only a single channel of
EEG, either on the prefrontal cortex (FP1) location or in the ear canal. Therefore,
we will need to develop new analytic techniques to both (i) assess improvements
in authentication accuracy due to the increased channels of data, and (ii) assess
relative contributions of individual electrode locations to authentication accuracy.
Finally, we will evaluate the usability of custom-fit Ear EEG authentication along
several dimensions. They include the comfort and fit of the earpieces, the
preparatory steps of using the devices, the ease and repeatability of the
authentication tasks, and the recall rates of the personal secrets.
\section{{\bfseries\sffamily TODO} Preliminary results}
\label{sec:org8cc774c}

We performed a very small pilot study (n=2) to better assess our projects' feasibility.
Our cursory analysis indicates that we can successfully
detect EEG signals from the ear (Section 5.1), that these signals can be used
for reliable authentication among two people (Section 5.2), and that the success
of the authenticator relies on the user's chosen secret, and not just the inherence
factor of the user's unique signal (Section 5.3).

\subsection{{\bfseries\sffamily TODO} Data collection}
\label{sec:org758093f}
\subsection{{\bfseries\sffamily TODO} Validation}
\label{sec:org7729653}
\subsection{Authentication performance}
\label{sec:org9e9cdb3}

Following [5], we use logarithmic binning to produce
compressed feature vectors of a variable size. This technique
has been show to offer robust, linear classifiability in healthy
subjects. It is unique in its use of the entire frequency
spectrum. Since EEG activity is associated with frequencies
from 1-40Hz, we presume this range contains the majority of
relevant signal. However, we do not rule out the possibility
that useful signal exists in other frequency ranges. Muscular
activity, for example, might be correlated with mental gestures
in some cases. Logarithmic binning produces feature vectors
biased toward known sources of signal, while still including
data points from outside this frequency range that may be
informative.

We analyzed the EEG signals collected during the tasks
using a support vector classifier (SVC). Since past work has
shown that classification tasks in EEG-based BCI are linear
[25], we used XGBoost, a popular tool for generating
ensemble linear classifiers. For each task, for each participant, 
100 seconds of data were
collected in total across 10 trials of 10 seconds each, 
resulting in 30 samples per participant, per task,
following preprocessing.

\begin{table}[htbp]
\caption{Authentication accuracy for each sensor position. Left and right ears were a composite of three electrode positions along the helix, front of the ear canal, and back of the ear canal.}
\centering
\begin{tabular}{lrrrrrr}
task & Left ear &  & Right Ear &  & fp1 & \\
\hline
 & FAR & FRR & FAR & FRR & FAR & FRR\\
\hline
speech & 0 & 0 & 0 & 0 & 0 & 0\\
face & 0 & 0 & 0 & 0.002 & 0 & 0\\
breathe & 0 & 0 & 0 & 0 & 0 & 0\\
listennoise & 0 & 0 & 0 & 0 & 0 & 0\\
song (eyes open) & 0 & 0 & 0 & 0 & 0 & 0\\
song & 0 & 0 & 0 & 0 & 0 & 0\\
sequence & 0 & 0 & 0 & 0 & 0 & 0\\
listentone & 0 & 0 & 0 & 0.009 & 0 & 0\\
breathe (eyes open) & 0.039 & 0 & 0 & 0 & 0 & 0\\
sport & 0.039 & 0.036 & 0 & 0 & 0 & 0\\
\end{tabular}
\end{table}

Finally, for each subject, for each task, we trained a binary classifier 
in the following manner: the right subject, performing the right task, were taken
as positive examples. The wrong person, performing any task, were taken as negative
examples. For a random, balanced subsample of those groups, we trained an ensemble
binary classifier with XGboost. For the remainder of the data, we tested the 
classifier's accuracy, measuring the false acceptance rate (FAR) and the false
rejection rate (FRR) (Table 1).

Overall, FAR and FRR were extremely low across the board. The right ear 
performed better than the left ear (possibly because the reference was on
the left ear, thus furthest from the right ear). In line with the 
results of prior work, Fp1 performed better than either the left or the right ear,
achieving perfect FAR and FRR scores on all tasks.

\subsection{Disentangling inherence and knowledge}
\label{sec:org310d6ff}

@@

\begin{table}[htbp]
\caption{FARs for right-person, wrong-task, and p-values corresponding to confidence that these FARs were drawn from the same distribution as from the right-person-right-task trials.}
\centering
\begin{tabular}{lrrr}
Task & Right ear & Left ear & fp1\\
\hline
speech & 0.311 & 0.116 & 0\\
face & 0.355 & 0.055 & 0\\
breathe & 0 & 0.240 & 0\\
listennoise & 0.322 & 0.078 & 0\\
song\(_{\text{o}}\) & 0 & 0.166 & 0\\
song & 0 & 0.211 & 0\\
sequence & 0.433 & 0 & 0\\
listentone & 0 & 0.333 & 0\\
breathe\(_{\text{o}}\) & 0.254 & 0.129 & 0\\
sport & 0.222 & 0.135 & 0\\
\hline
\textbf{p-value} & \textbf{*0.0076} & \textbf{*0.009} & N/A\\
\end{tabular}
\end{table}

Our low p-values (Table 2) indicate that the passthought, as well as the inherence
factor associated with the custom-fit EEG earbud, both contribute to the classifier
performance discussed in Section 5.2. We are confident, then, in our claim that this work
could potentially yield multiple-factor authentication in a single step. However, we
will need to collect a great deal more data to substantiate this claim rigorously.

\section{Schedule and Budget}
\label{sec:org06119b2}
We propose a 12-month schedule with two graduate students working on the
project:

\begin{itemize}
\item Months 1-6: hardware development for custom-fit earpiece; integration with OpenBCI; testing
\item Months 1-6: software integration between OpenBCI, PsychoPy, and Indra; design of new authentication tasks and implementation in PsychoPy
\item Months 7-8: experimental data collection
\item Months 9-12: data analysis; write and submit research papers
\end{itemize}
\section{References}
\label{sec:orgcb67560}
\setlength\parindent{0pt}

[1]
J. Chuang, One-Step Two-Factor Authentication with Wearable Bio-Sensors, Workshop on
"Who are you?! Adventures in Authentication" (WAY'14), 10th USENIX Symposium on
Usable Privacy and Security (SOUPS'14), 2014.
\hspace{0pt} \\

[2]
J. Chuang, H. Nguyen, C. Wang, B. Johnson, I Think, Therefore I Am: Usability and
Security of Authentication Using Brainwaves, Workshop on Usable Security (USEC'13),
17th Int. Conference on Financial Cryptography and Data Security (FC’13), 2013.
\hspace{0pt} \\

[3]
B. Johnson, T. Maillart, J. Chuang, My Thoughts are Not Your Thoughts: Robustness of
Brainwave Signal Authentication Against Impersonation Attacks, Workshop on Usable
Privacy \& Security for wearable and domestic Ubiquitous Devices, ACM UbiComp, 2014.
\hspace{0pt} \\

[4]
M. Curran, J. Yang, N. Merrill, J. Chuang. Passthoughts Authentication with Low Cost
EarEEG. Proc. 38th Intl. Conf. of IEEE Engineering in Medicine and Biology Society
(EMBC 2016), Aug. 2016.
\hspace{0pt} \\

[5]
N. Merrill, Maillart, Johnson, J. Chuang, Improving Physiological Signal Classification Using
Logarithmic Quantization and a Progressive Calibration Technique, Proc. 2nd Intl. Conf. on
Physiological Computing Systems (PhyCS'15), Feb. 2015.
\hspace{0pt} \\

[6]
J. Thorpe, P. van Oorschot, and A. Somayaji. Pass-thoughts: Authenticating with our
minds. In Proceedings of the New Security Paradigms Workshop (NSPW), 2005.
\hspace{0pt} \\

[7]
M. Poulos, M. Rangoussi, N. Alexandris, and A. Evangelou. Person identification from the
EEG using nonlinear signal classification. Methods of Information in Medicine, 2002.
\hspace{0pt} \\

[8]
S. Marcel and J. del R. Millan. Person authentication using brainwaves (EEG) and
maximum a posteriori model adaptation. IEEE Transactions on Pattern Analysis and
Machine Intelligence, 29(4), April 2007.
\hspace{0pt} \\

[9]
R. Palaniappan. Two-stage biometric authentication method using thought activity brain
waves. International Journal of Neural Systems, 18(1):59–66, 2008.
\hspace{0pt} \\

[10]
C. Ashby, A. Bhatia, F. Tenore, and J. Vogelstein. Low-cost electroencephalogram (EEG)
based authentication. In Proc. of 5th Int. IEEE EMBS Conf. on Neural Engineering, 2011.
\hspace{0pt} \\

[11]
D. Looney, C. Park, P. Kidmose, M. L. Rank, M. Ungstrup, K. Rosenkranz, and D. P.
Mandic, “An in-the-ear platform for recording electroencephalogram,” in Proc. Int. Conf.
IEEE Eng. Med. Biol. Soc., 2011, pp. 6682–6885.
\hspace{0pt} \\

[12]
D. Looney, P. Kidmose, C. Park, M. Ungstrup, M. Rank, K. Rosenkranz, and D. Mandic,
“The in-the-ear recording concept,” IEEE Pulse, vol. 3, no. 6, pp. 32–42, Nov./Dec. 2012.
\hspace{0pt} \\

[13]
P. Kidmose, D. Looney, M. Ungstrup, M.L. Rank, D.P. Mandic, “A study of evoked
potentials from ear-EEG,” IEEE Trans. Biomed. Eng. 60(10), pp. 2824–2830, 2013.
\hspace{0pt} \\

[14]
P. Kidmose, D. Looney, and D. P. Mandic, “Ear-EEG from generic earpieces: a feasibility
study,” in Proc. Int. Conf. IEEE Eng. Med. Biol. Soc., 2013, pp. 543-546.
\hspace{0pt} \\

[15] The Aware. \url{http://efitaware.com} [Online; accessed 22-Oct-2016].
\hspace{0pt} \\

[16] F. Monrose and A. Rubin. Authentication via keystroke dynamics. In Proceedings of the 4th
ACM conference on Computer and communications security, pages 48–56. ACM, 1997.
\hspace{0pt} \\

[17]
K. Stevens et al. Speaker authentication and identification: a comparison of spectrographic
and auditory presentations of speech material. The Journal of the Acoustical Society of
America 44.6 (1968): 1596-1607.
\hspace{0pt} \\

[18] Nymi. \url{https://nymi.com} [Online; accessed 22-Oct-2016].
\hspace{0pt} \\

[19] E. Strickland. In-Ear EEG Makes Unobtrusive Brain-Hacking Gadgets a Real Possibility.
IEEE Spectrum, 7/7/2016.
\hspace{0pt} \\

[20]
N. Merrill, M. Curran, J. Yang, J. Chuang. Classifying Mental Gestures with In-Ear EEG.
Proc. 13th IEEE Intl. Conf. on Wearable and Implantable Body Sensor Networks (BSN
2016), Jun. 2016.
\hspace{0pt} \\

[21]
E. Sedenberg, J. Chuang, D. Mulligan. Designing Commercial Therapeutic Robots for
Privacy Preserving Systems and Ethical Research Practices Within the Home. Intl. J. of
Social Robotics, Aug. 2016.
\hspace{0pt} \\

[22] E. Sedenberg et al. A Window into the Soul: Biosensing in Public. Under review, 2017.
\hspace{0pt} \\

[23] R. Wong et al. “All that happens must be known”: Eliciting Values and Conceptions of
Privacy using Science Fiction. Under review, 2017.
\hspace{0pt} \\

[24]
R. Wong et al. Real-Imaginary Entanglements: Using Science Fiction and Design Fiction to
Explore and Question Sensing and Tracking Technologies. Under review, 2017.
\hspace{0pt} \\

[25] D. Garrett, D. Peterson, C. Anderson, and M. Thaut, “Comparison
of linear, nonlinear, and feature selection methods for eeg
signal classification,” IEEE Transactions on Neural Systems and
Rehabilitation Engineering, vol. 11, no. 2, pp. 141–144, Jun. 2003.
[Online]. Available: \url{http://ieeexplore.ieee.org/lpdocs/epic03/wrapper}.
htm?arnumber=1214704
\hspace{0pt} \\
\end{document}
